Initial environmental impacts of Piney Point wastewater discharge into Tampa Bay, Florida

### 2021-08-17 manu-draft.Rmd
water quality comparison table added

data(rstrnpts)
load(file = here('tables/wqsumtab.RData'))
load(file = here('tables/stktab.RData'))

@@

@@

* Table \@ref(tab:stktab) Stack characteristics
* Table \@ref(tab:wqsumtab) water quality data collected and summarized
* Table 3 Tukey multiple comparisons of water quality by week/area, with median/min/max
* Table 4 Seagrass/macroalgae freq. occurrence summaries

@@

```{r stktab}
cap.val <- 'Measured concentrations from the phosphogypsum stack (NGS-S) at Piney Point on April 9th, 2021 for relevant water quality variables compared to normal annual means (min, max) for concentrations in lower Tampa Bay.  Normal means are based on data for a baseline period from 2006 to 2020 from long-term monitoring stations in lower Tampa Bay collected monthly by Hillsborough County Environmental Protection Commission.'
knitr::kable(stktab, booktabs = T, caption = cap.val)
```

@@

>>>>

data(rstrnpts)
load(file = here('tables/wqsumtab.RData'))
load(file = here('tables/stktab.RData'))
load(file = here('tables/wqcmptab.RData'))

@@

For total nitrogen, chlorophyll-a, and secchi depth, differences in concentrations between months within each area (Figure \@ref(fig:map)a) were evaluated using a Kruskal-Wallis one-way analysis of variance (ANOVA) followed by multiple comparisons using 2-sided Mann-Whitney U tests [@Hollander13]. Probability values were adjusted using the sequential Bonferroni method described in [@Holm79] to account for the increased probability of Type I error rates with multiple comparisons. An adjusted p-value < 5\% ($\alpha$ = 0.05) was considered a significant difference between months.

@@

* Table \@ref(tab:stktab) Stack characteristics
* Table \@ref(tab:wqsumtab) water quality data collected and summarized
* Table \@ref(tab:wqcmptab) Multiple comparisons of water quality by month/area, with median/min/max
* Table 4 Seagrass/macroalgae freq. occurrence summaries

@@

```{r stktab}
cap.val <- 'Measured concentrations from the phosphogypsum stack (NGS-S) at Piney Point on April 9th, 2021 for relevant water quality variables compared to normal annual means (min, max) for concentrations in lower Tampa Bay.  Normal medians are based on data for a baseline period from 2006 to 2020 from long-term monitoring stations in lower Tampa Bay collected monthly by Hillsborough County Environmental Protection Commission.'
knitr::kable(stktab, booktabs = T, caption = cap.val)
```

@@

```{r wqcmps}
cap.val <- 'Comparison of total nitrogen, chlorophyll-a, and secchi depth by areas of interest (Figure \\@ref(fig:map)a) and month.  Multiple comparisons with Mann-Whitney U tests were used to evaluate pairwise monthly concentrations for each water quality variable in each area.  Rows that share a letter within each area and water quality variable combination have concentrations that are not significantly different at $\\alpha$ = 0.05. Probability values were adjusted using the Bonferroni method in @Holm79.'
knitr::kable(wqcmptab, booktabs = T, caption = cap.val)
```
